Cataclysmic variables are a key population of gravitational wave sources for LISA

### 2023-06-16 src/tex/ms.tex
clarify not only detached

%\kb{commented out what I think is a rogue \pjg}
In order to determine how much the $1~\rm{kpc}$ CV population contributes to the Galactic GW foreground for \lisa\, we must include the effects of the Galactic detached double WD population as well as the \lisa\ constellation orbit. We do this using \texttt{ldasoft} \citep{ldasoft}. For this study, we use the same Galactic population as was used for the LDC2a-v1 data set provided by the \lisa\ Data Challenges (LDCs)~\citep{le_jeune_maude_2022_7132178} which \textbf{consists of both detached and interacting} double WD binaries. We consider two population cases, one which contains \textbf{only the double WD binaries from the LDC} and one which adds our $1~\rm{kpc}$ mock population of CVs before modeling the \lisa\ response to the combined signal of each Galactic binary after four years of operations. Together, these two simulations allow us to capture the effects of considering the $1~\rm{kpc}$ CV population in the Galactic foreground.

>>>>

%\kb{commented out what I think is a rogue \pjg}
In order to determine how much the $1~\rm{kpc}$ CV population contributes to the Galactic GW foreground for \lisa\, we must include the effects of the Galactic double WD population as well as the \lisa\ constellation orbit. We do this using \texttt{ldasoft} \citep{ldasoft}. For this study, we use the same Galactic population as was used for the LDC2a-v1 data set provided by the \lisa\ Data Challenges (LDCs)~\citep{le_jeune_maude_2022_7132178} which \textbf{consists of both detached and interacting} double WD binaries. We consider two population cases, one which contains \textbf{only the double WD binaries from the LDC} and one which adds our $1~\rm{kpc}$ mock population of CVs before modeling the \lisa\ response to the combined signal of each Galactic binary after four years of operations. Together, these two simulations allow us to capture the effects of considering the $1~\rm{kpc}$ CV population in the Galactic foreground.
